The transiting dust clumps in the evolved disk of the Sun-like UXOr RZ~Psc

### 2016-08-31 ms.tex
tex in MNRAS format

\author[Grant M. Kennedy et al]{Grant M. Kennedy\thanks{Email:
    \href{mailto:gkennedy@ast.cam.ac.uk}{gkennedy@ast.cam.ac.uk}}$^1$,
  Matthew Kenworthy$^2$,
  Joshua Pepper$^3$, \newauthor
  Joseph E. Rodriguez$^{4,5}$, 
  Robert Siverd$^6$, \&
  Keivan G. Stassun$^{5,7}$ \\
  $^1$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3
  0HA, UK \\
  $^2$ Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the
  Netherlands \\
  $^3$ Department of Physics, Lehigh University, 16 Memorial Drive East, Bethlehem, PA
  18015, USA \\
  $^4$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, MS-78, Cambridge, MA
  02138, USA \\
  $^5$ Department of Physics and Astronomy, Vanderbilt University, 6301 Stevenson Center,
  Nashville, TN 37235, USA \\
  $^6$ Las Cumbres Observatory Global Telescope Network, 6740 Cortona Dr., Suite 102, Santa
  Barbara, CA 93117, USA \\
  $^7$ Department of Physics, Fisk University, 1000 17th Avenue North, Nashville, TN
  37208, USA \\
}
\maketitle

@@

To study the temporal variability of RZ~Psc we use two seasons of public data from the
Wide-Angle Search for Planets \citep[WASP,][]{2006PASP..118.1407P}, and nine seasons of
data from the Kilodegree Extremely Little Telescope North
\citep[KELT-North,][]{2007PASP..119..923P}. We also collected, but ultimately did not
use, photometric observations of RZ~Psc from a wide variety of other sources \citep[][,
the Catalina Sky Survey, the American Association of Variable Star Observers, the All-Sky
Automated
Survey]{1994AJ....108.1906H,1973IBVS..783....1K,1980PZ.....21..310K,1985PZ.....22..181Z,1991Afz....34..333K,1997AcA....47..467P,2014Ap.....57..491P}. Most
of these other data have been previously published and their collation here is largely
for the benefit of others. This compilation contains nearly all data for which tables
have been published, but aside from the Harvard plate photometry published by
\citet{1999A&AS..140..293G} we have not sought other photometry so the light curve
remains incomplete. All photometry we collected is tabulated in the Appendix.

@@

We thank Joachim G\"urtler for sharing photometry from the Sonneberg and Harvard Plates
in a palatable form, AAVSO observers for monitoring RZ~Psc, and Simon Hodgkin and Mark
Wyatt for useful discussions. This paper makes use of data from the DR1 of the WASP data
\citep{2010A&A...520L..10B} as provided by the WASP consortium, and the computing and
storage facilities at the CERIT Scientific Cloud, reg. no. CZ.1.05/3.2.00/08.0144 which
is operated by Masaryk University, Czech Republic. GMK is supported by the Royal Society
as a Royal Society University Research Fellow.

>>>>

\author[Grant M. Kennedy et al]{Grant M. Kennedy\thanks{Email:
    \href{mailto:gkennedy@ast.cam.ac.uk}{gkennedy@ast.cam.ac.uk}}$^1$,
  Matthew A. Kenworthy$^2$,
  Joshua Pepper$^3$, \newauthor
  Joseph E. Rodriguez$^{4,5}$, 
  Robert J. Siverd$^6$, \&
  Keivan G. Stassun$^{5,7}$ \\
  $^1$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3
  0HA, UK \\
  $^2$ Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the
  Netherlands \\
  $^3$ Department of Physics, Lehigh University, 16 Memorial Drive East, Bethlehem, PA
  18015, USA \\
  $^4$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, MS-78, Cambridge, MA
  02138, USA \\
  $^5$ Department of Physics and Astronomy, Vanderbilt University, 6301 Stevenson Center,
  Nashville, TN 37235, USA \\
  $^6$ Las Cumbres Observatory Global Telescope Network, 6740 Cortona Dr., Suite 102, Santa
  Barbara, CA 93117, USA \\
  $^7$ Department of Physics, Fisk University, 1000 17th Avenue North, Nashville, TN
  37208, USA \\
}
\maketitle

@@

To study the temporal variability of RZ~Psc we use two seasons of public data from the
Wide-Angle Search for Planets \citep[WASP,][]{2006PASP..118.1407P}, and nine seasons of
data from the Kilodegree Extremely Little Telescope North
\citep[KELT-North,][]{2007PASP..119..923P}. We also collected, but ultimately did not
use, photometric observations of RZ~Psc from a wide variety of other sources \citep[][,
the Catalina Sky Survey, the American Association of Variable Star Observers, the All-Sky
Automated
Survey]{1994AJ....108.1906H,1973IBVS..783....1K,1980PZ.....21..310K,1985PZ.....22..181Z,1991Afz....34..333K,1997AcA....47..467P,2014Ap.....57..491P}. Most
of these other data have been previously published and their collation here is largely
for the benefit of others. This compilation contains nearly all data for which tables
have been published, but aside from the Harvard plate photometry published by
\citet{1999A&AS..140..293G} we have not sought other photometry so the light curve
remains incomplete.\footnote{Normalised photometry is available at
  \href{https://github.com/drgmk/rzpsc}{https://github.com/drgmk/rzpsc}}

@@

Data and code used in the preparation of this contribution can be found online at
\href{https://github.com/drgmk/rzpsc}{https://github.com/drgmk/rzpsc}.

We have no competing interests.

GMK initiated the project, collated data, did most of the analysis, and wrote the
paper. MAK contributed early ideas and the iterative event finding method. KGS provided
independent SED models to test for a UV excess. As members of the KELT collaboration, JP,
JER, RJS, and KGS acquired the time-series photometry. All co-authors provided input on
the style and content of the manuscript.

We thank Joachim G\"urtler for sharing photometry from the Sonneberg and Harvard Plates
in a palatable form, AAVSO observers for monitoring RZ~Psc, and Simon Hodgkin and Mark
Wyatt for useful discussions. This paper makes use of data from the DR1 of the WASP data
\citep{2010A&A...520L..10B} as provided by the WASP consortium, and the computing and
storage facilities at the CERIT Scientific Cloud, reg. no. CZ.1.05/3.2.00/08.0144 which
is operated by Masaryk University, Czech Republic.

GMK is supported by the Royal Society as a Royal Society University Research Fellow. MAK
is employed as a lecturer at the Leiden Observatory. JP is employed as a lecturer at
Lehigh University. JER is funded as a Future Faculty Leaders Fellow at the
Harvard-Smithsonian Center for Astrophysics. RS is employed as an Instrumentation
Scientist for the Las Cumbres Observatory Global Telescope Network. KGS is funded as a
lecturer at Vanderbilt University.
